problem years

### 2024-08-13 src/problem_years.Rmd
legend

ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  # scale_fill_discrete_c4a_cat(name = "%", palette = "parks.charmonix",
  #                             na.translate = FALSE) +
  scale_fill_manual(values = palette_new, na.value="white", breaks = NULL, drop = F) +
  theme_minimal() +
  theme(panel.grid.major = element_line(colour = "transparent"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank()) +
  #guides(fill = guide_legend(reverse = TRUE)) +
  labs(title = "LISA, websites per firm in a LA") + 
  theme(legend.title=element_blank())

theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      rect = element_blank(),
      plot.margin = unit(c(0, 0, 0, 0), "cm"))

@@

>>>>

ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  # scale_fill_discrete_c4a_cat(name = "%", palette = "parks.charmonix",
  #                             na.translate = FALSE) +
  scale_fill_manual(values = palette_new, na.value="white", breaks = NULL, drop = F) +
  theme_minimal() +
  theme(panel.grid.major = element_line(colour = "transparent"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank()) +
  #guides(fill = guide_legend(reverse = TRUE)) +
  labs(title = paste0("LAD, ", t)) + #"LISA, websites per firm in a LA") + 
  theme(legend.title=element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        plot.title = element_text(hjust = 0.5)) +
  theme(plot.title = element_text(size=20, face = "bold"))

# theme(axis.text.x = element_blank(),
#       axis.text.y = element_blank(),
#       axis.ticks = element_blank(),
#       rect = element_blank())

@@

### lisa map legend
```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/LA/lisa_level_pc", n, "_la_legend.png") 
legend <- ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  scale_fill_manual(values = palette_new, na.value="white", drop = F, name = NULL) +
  theme_minimal() +
  theme(legend.position="right",
        legend.margin=ggplot2::margin(c(1,1,1,1)))

legend <- cowplot::get_legend(legend)

leg <- as_ggplot(legend)
leg <- leg + theme(
  legend.margin=ggplot2::margin(c(0,0,0,0)))
#ggsave(path.out, width = 5, height = 0.4, bg='#ffffff')
ggsave(path.out, width = 1, height = 1.4, bg='#ffffff')
```
